Continuous Deductive Reasoning over Streamed RDF Data

### 2015-11-17 article.tex
directly address points regarding count-based windows, persistent facts being annotated with the instant 0 and contradictions invalidating an entire window state.

Based on this definition of streams, we go on to define the notion of
sliding windows over streams, as well as states of those windows at
specific instants.  We do not consider count-based window functions, as
these serve a semantic purpose at high specificity, e.g. \emph{retain
the last ten buses to stop at a specific stop}.  In contrast, as will be
formally described in \refdef{continuous datalog: CDP}, we consider only
the application of the \emph{entirety of a rule set} within the
consecutive states of one (or more) window(s); in this context, an
example application of a count-based window might be to \emph{determine
the implications of the last hundred facts reported by a sensor network,
given some background knowledge regarding that network}.

@@

We initially take a {\em Continuous Datalog program} (henceforth a
C-Datalog program) $\Pi^C = \langle R, F^0, S \rangle$ to be a tuple
which comprises a finite set of rules $R$, a finite set of persistent/static
fact instances $F^0$ (all of which have the instant $0$, meaning that they
cannot appear in any state of any window, by
\refdef{continuous datalog: window} and Axioms~\ref{axiom:continuous datalog: window range leq 0} and
\ref{axiom:continuous datalog: window start leq 0}) and an in-order stream
of fact instances $S$.  It should be noted that, in practice, data may be
drawn from more than one source, and so $S$ may be a union of $n$ in-order
streams $S_1,\dots,S_n$ without altering the semantics presented here.

@@

An \emph{inconsistent state} of a C-Datalog program is any instantaneous
state $\Pi^{C,r}_i$ that is unsatisfiable, i.e. that contains at least
one contradiction.  Such a state has no entailment.

>>>>

Based on this definition of streams, we go on to define a notion of
sliding time-based windows over streams, as well as states of those windows at
specific instants.  Every fact instantiated in the state of such a window at a
given instant is considered to be true at that instant.  We do not consider count-based
window functions, as the state of such windows (and therefore the truth of the
facts instantiated therein) is determined by the contents of the stream as a
whole, which is a form of aggregation that contrasts with that of time-based
windows: where the states of the latter are determined by some
function of each element of the stream (the time from the instant of its
appearance thereon), the states of the former are determined by a function of
the stream itself.  This is more similar to the aggregation functions of SQL,
such as $count()$, $max()$, etc., which are not part of the semantics of
positive Datalog or (outside of specific heavily restricted cases) OWL 2 RL
\citep{w3cowl2profiles}.

% serve a semantic purpose at high specificity, e.g. \emph{retain
% the last ten buses to stop at a specific stop}.  In contrast, as will be
% formally described in \refdef{continuous datalog: CDP}, we consider only
% the application of the \emph{entirety of a rule set} within the
% consecutive states of one (or more) window(s); in this context, an
% example application of a count-based window might be to \emph{determine
% the implications of the last hundred facts reported by a sensor network,
% given some background knowledge regarding that network}.

@@

We initially take a {\em Continuous Datalog program} (henceforth a
C-Datalog program) $\Pi^C = \langle R, F^0, S \rangle$ to be a tuple
which comprises a finite set of rules $R$, a finite set of persistent/\emph{static}
fact instances $F^0$ (all of which have the instant $0$, meaning that the facts
instantiated are recognised to be true from the beginning of time and cannot
appear in any state of any window, by \refdef{continuous datalog: window} and
Axioms~\ref{axiom:continuous datalog: window range leq 0} and
\ref{axiom:continuous datalog: window start leq 0}) and an in-order stream
of fact instances $S$.  It should be noted that, in practice, data may be
drawn from more than one source, and so $S$ may be a union of $n$ in-order
streams $S_1,\dots,S_n$ without altering the semantics presented here.

@@

An \emph{inconsistent state} of a C-Datalog program is any instantaneous
state $\Pi^{C,r}_i$ that is unsatisfiable, i.e. that contains at least
one contradiction.  Such a state has no entailment.  As this is not often
desirable in real-world applications, policies may feasibly be employed in
practise to eliminate facts from a window prematurely, with a view to making
an inconsistent state satisfiable. However, such policies are not discussed
here as the policy implemented (if any) depends upon the nature of the
application.
